Abstract Plots

### 2021-07-22 Abstract.Rmd
Cleaned dilution plots.

for (x in seq(10, num.mut-1, by = 10)){
  sample.sig6 <- create_signature_sample_vector(cosmic.sig6, x)
  sig6.truth <- rep("MMR", x)
  sample.ffpe <- create_signature_sample_vector(ffpe.sig, num.mut-x)
  ffpe.truth <- rep("FFPE", num.mut-x)
  test <- get_classification_df(list(sample.sig6, sample.ffpe), c("MMR","FFPE"),
                                list(cosmic.sig6, ffpe.sig))
  classification <- test %>%
    mutate(trueBinary = ifelse(truth == "MMR",1,0))

@@

for (x in seq(10, num.mut-1, by = 10)){
  sample.sig4 <- create_signature_sample_vector(cosmic.sig4, x)
  sig4.truth <- rep("Tobacco", x)
  sample.ffpe <- create_signature_sample_vector(ffpe.sig, num.mut-x)
  ffpe.truth <- rep("FFPE", num.mut-x)
  test <- get_classification_df(list(sample.sig4, sample.ffpe), c("Tobacco","FFPE"),
                                list(cosmic.sig4, ffpe.sig))
  classification <- test %>%
    mutate(trueBinary = ifelse(truth == "Tobacco",1,0))

@@

for (iteration in 1:20){
  sens.MMR <- performance(test.MMR, measure = "sens")

@@

for(iteration in 1:20){
  sens.tob <- performance(test.tob, measure = "sens")

@@

```{r}
plot(1:99, sens.MMR.vec, ylim = c(0,1), xlab = "Percent of each signature", 
     ylab = "Sensitivity value", type = "l", main = "Comparing performance characteristics")
lines(1:99, sens.tob.vec, lty = 2)
abline(h = 0.85, col = "red")
legend("bottomright", c("MMR sensitivity", "Tobacco sensitivity", 
                        "Satisfactory Sensitivity"),
       lty = c(1,2,1), col = c("black", "black", "red"))
```

@@

```{r}
plot(1:99, spec.MMR.vec, ylim = c(0,1), xlab = "Percent of each signature", 
     ylab = "Specificity value", type = "l", main = "Comparing performance characteristics")
lines(1:99, spec.tob.vec, lty = 2)
abline(h = 0.85, col = "red")
legend("bottomleft", c("MMR specificity", "Tobacco specificity", 
                       "Satisfactory Specificity"),
       lty = c(1,2,1), col = c("black", "black", "red"))
```

>>>>

for (x in seq(10, num.mut-1, by = 10)){
  sample.ffpe <- create_signature_sample_vector(ffpe.sig, x)
  ffpe.truth <- rep("FFPE", x)
  sample.sig6 <- create_signature_sample_vector(cosmic.sig6, num.mut-x)
  sig6.truth <- rep("MMR", num.mut-x)
  test <- get_classification_df(list(sample.sig6, sample.ffpe), c("MMR","FFPE"),
                                list(cosmic.sig6, ffpe.sig))
  classification <- test %>%
    mutate(trueBinary = ifelse(truth == "MMR",1,0))

@@

for (x in seq(10, num.mut-1, by = 10)){
  sample.ffpe <- create_signature_sample_vector(ffpe.sig, x)
  ffpe.truth <- rep("FFPE", x)
  sample.sig4 <- create_signature_sample_vector(cosmic.sig4, num.mut-x)
  sig4.truth <- rep("Tobacco", num.mut-x)
  test <- get_classification_df(list(sample.sig4, sample.ffpe), c("Tobacco","FFPE"),
                                list(cosmic.sig4, ffpe.sig))
  classification <- test %>%
    mutate(trueBinary = ifelse(truth == "Tobacco",1,0))

@@

for (iteration in 1:50){
  sens.MMR <- performance(test.MMR, measure = "sens")

@@

for(iteration in 1:50){
  sens.tob <- performance(test.tob, measure = "sens")

@@

```{r}
sensitivity = append(sens.MMR.vec, sens.tob.vec)
signature.sens = append(rep("MMR", length(sens.MMR.vec)),
                        rep("Tobacco", length(sens.tob.vec)))
dilution = append(1:99, 1:99)
sens.df <- data.frame(dilution, sensitivity, signature.sens)

ggplot(data = sens.df, mapping = aes(x = dilution, 
                                     y = sensitivity, 
                                     color = signature.sens)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Sensitivity as a function of FFPE noise",
       x = "Percent of FFPE noise in samples",
       y = "Sensitivity value",
       color = "True signal")
```

@@

```{r}
specificity = append(spec.MMR.vec, spec.tob.vec)
signature.spec = append(rep("MMR", length(sens.MMR.vec)),
                        rep("Tobacco", length(spec.tob.vec)))
dilution = append(1:99, 1:99)
spec.df <- data.frame(dilution, specificity, signature.spec)

ggplot(data = spec.df, mapping = aes(x = dilution, 
                                     y = specificity, 
                                     color = signature.sens)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Specificity as a function of FFPE noise",
       x = "Percent of FFPE noise in samples",
       y = "Specificity value",
       color = "True signal")
```
